ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-04 paper.tex
more figures and added to sections

The goal of Editour is to allow a non-technical user to design audio tours
through a web app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map, edit those regions and assign media to each of
the drawn regions.

@@

% TODO update this figure
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

\subsubsection{Editour Frontend Implementation}
\label{sec:editourFrontendImplementation}

@@

@@

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google~Translate's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. Then, the user is prompted to
highlight where text appears in the photo. After the translation is complete,
the translated text appears in a separate UI element. In most cases, it is more
convenient and readable to have the translation appear in a separate scrollable
text box. This motivated the current design of the ``info buttons'' in ARuko.
Instead of placing text directly onto signage, we place a blue button with a
stylized ``\textit{i}'' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
on top of the content.
% TODO images for this section

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground. Atticus suggested that we
re-orient the model such that the ticket served as a back plane. This would
allow users to hold the ticket vertically, and view the Golden Pavilion floating
in front of the ticket. This allows users to place their hands under the base of
the Golden Pavilion model as if they were holding it; Vuforia's image tracking
is flexible enough such that the image target can be partially obscured by the
hand.

@@

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the noh performer into a new
Unity project. We did this two reasons. First,
we did not want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the
original project was made with a 2017 version of Unity, so we wanted to try to
import it into the most recent version so we would not risk running into any
deprecated features or functionalities. We did eventually get this method to
work, but the model of the noh performer was lacking a lot of the details that
the original model had. This was attributed to errors while importing the
original assets, so we decided to try making changes to the original NOxAR
project instead. 
% TODO could probably put an example pic here

Per Atticus's advice, we deleted any and all unnecessary elements from the scene
before proceeding. We also updated the Unity version of the project to the 2019
version we were using, and updated the version of Vuforia to the most recent
version, neither of which created any problems. The process of getting the model
to appear on ground plane detection instead of image target recognition was
relatively easy. We simply moved the model from an image target to a simulated
ground plane, added a plane detector component to the scene, and made sure the
Vuforia settings were in place for ground plane detection to work well. From
there, we just had to test the app a few times so we could properly scale the
model to life size. On Tuesday, September 17\textsuperscript{th}, we completed
the NOxAR ground plane adaptation to Atticus's satisfaction and sent him the
final APK file for the app.

>>>>

The goal of Editour is to allow a non-technical user to design audio tours
through a web app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map, edit those regions and assign media to each of
the drawn regions. Figure~\ref{fig:editour} shows a screenshot of the web
interface used to design tours.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{updated-editour.png}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

\subsubsection{Editour Frontend Implementation and Design}
\label{sec:editourFrontendImplementation}

@@

The look and feel of the Editour frontend was inspired from multiple sources.
The color scheme of the UI was inspired by the Super Famicom controller, which
can be seen in Figure~\ref{fig:superFamicomController}. The shape of the
``cards'' within the sidebar were inspired by the GitHub Kanban board on the
``Projects'' tab of a GitHub repo (which can be seen in
Figure~\ref{fig:kanbanBoard} in the Appendix).

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{super-famicom-controller.jpg}
    \caption[A Japanese Super Famicom controller.]{The inspiration for the
    colorscheme: a Japanese Super Famicom controller~\autocite{amos2017}.}
    \label{fig:superFamicomController}
\end{figure}

Since the frontend of Editour was implemented using basic web technologies, we
had access to the full power of CSS to style each element of the GUI. The
classes within CSS were designed so they could be reused easily and composed
with one another. If, for example, we needed to change the font of every element
that was styled like a button, we could do so by simply changing the
\texttt{font-family} attribute in a single CSS class. Consider the green bar
pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
order to inherit the visual descriptions of other UI elements. The four CSS
classes on this bar are \texttt{button}, \texttt{greenbutton},
\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
elements as the slightly raised, rounded rectangle that can be seen throughout
the UI. Additionally, all elements with the \texttt{button} class will have a
subtle ``press'' animation when being clicked on, since key frame animations can
also be defined in CSS. The default color of the button is red; the bottom of
the button is a slightly darker shade to give a 3D effect. Both of these colors
are conveniently stored as custom CSS variables, \texttt{--bg-color} and
\texttt{--bottom-color}. This allows another class to easily override these
colors. This is what the class \texttt{greenbutton} does; an HTML element with
the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
or \texttt{bluebutton} will be styled like a button and have a new color palette
applied. In order to differentiate the buttons that reveal subcards, the
\texttt{outlinebutton} class is used. This class takes the custom
\texttt{--bg-color} property and applies it to the border, drop shadow and text
color instead of the background. This class was also applied to the buttons that
can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
the \texttt{revealer} class changes the text from centered to left-justified
among other minor formatting adjustments. CSS allowed us to define the look and
feel programmatically with the need to create graphical assets using image
editing software. This means that anyone using the codebase of Editour for
different purposes can easily change the look and feel of the frontend by
changing the CSS.\footnote{This is allowed since Editour is free software, which
is discussed briefly in Section~\ref{sec:futureOfEditour}.}

@@

Currently, there is no way to download a previous version of a tour directly
from the UI, despite the fact that the backend automatically saves timestamped
backups of tours as they are uploaded. Our team is able to recover backups by
copying files directly from the server. However, we would like to design an
intuitive version browser in the frontend so that any user can recover previous
versions of their tour.

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google~Translate's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. This will sometimes produce
useless results, as seen in Figure~\ref{fig:translateInstant}. Then, the user
is prompted to highlight where text appears in the photo by dragging lines onto
the screen where text appears, as seen in Figure~\ref{fig:translateScan}. After
the translation is complete, the translated text appears in a separate UI
element, which can be seen in Figure~\ref{fig:translateFinalCard}. In most
cases, it is more convenient and readable to have the translation appear in a
separate scrollable text box. This motivated the current design of the ``info
buttons'' in ARuko. Instead of placing text directly onto signage, we place a
blue button with a stylized ``\textit{i}'' in the center. By tapping on this
button, a separate UI element will appear containing the translated text. Since
this button is cast into the world using the AR camera, the button appears to
be placed directly on top of the content.

% TODO make it so these images don't appear so far away (thank you LaTeX)
\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
	\caption{Google Translate camera feature in ``instant'' mode.}
	\label{fig:translateInstant}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
	\caption{Google Translate camera feature in ``scan'' mode}
	\label{fig:translateScan}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
	\caption{The final page seen after using ``scan'' mode in Google Translate}
	\label{fig:translateFinalCard}
\end{figure}

Additionally, we would not try to use any text recognition or translation APIs
to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
that this kind of technology needs to mature before it is completely usable,
especially for Japanese. Instead, we had Atticus share a Google Sheets
spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
his decision making process about each translation. Once this time-intensive
labor was completed, we took each field of translated text from the spreadsheet
and implemented it directly into the app, associating each translation with the
correct image target.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground, as depicted in
Figure~\ref{fig:kinkakujiHorizontal}. Atticus suggested that we re-orient the
model such that the ticket served as a back plane, as pictured in
Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically,
and view the Golden Pavilion floating in front of the ticket. This allows users
to place their hands under the base of the Golden Pavilion model as if they were
holding it; Vuforia's image tracking is flexible enough such that the image
target can be partially obscured by the hand.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
	\label{fig:kinkakujiHorizontal}
\end{figure}

@@

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the noh performer into a new
Unity project. We did this two reasons. First,
we did not want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the
original project was made with a 2017 version of Unity, so we wanted to try to
import it into the most recent version so we would not risk running into any
deprecated features or functionalities. We did eventually get this method to
work, but the model of the noh performer was lacking a lot of the details that
the original model had. This was attributed to errors while importing the
original assets, so we decided to try making changes to the original NOxAR
project instead.

Per Atticus's advice, we deleted any and all unnecessary elements from the scene
before proceeding. We also updated the Unity version of the project to the 2019
version we were using, and updated the version of Vuforia to the most recent
version, neither of which created any problems. The process of getting the model
to appear on ground plane detection instead of image target recognition was
relatively easy. We simply moved the model from an image target to a simulated
ground plane, added a plane detector component to the scene, and made sure the
Vuforia settings were in place for ground plane detection to work well. From
there, we just had to test the app a few times so we could properly scale the
model to life size. On Tuesday, September 17\textsuperscript{th}, we completed
the NOxAR ground plane adaptation to Atticus's satisfaction and sent him the
final APK file for the app. Figure~\ref{fig:noArWorking} shows how the final
working version of the NOxAR app.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{no-ar-working.jpg}
	\caption{Noh artist dancing on the ground plane of the scene}
	\label{fig:noArWorking}
\end{figure}
